Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-11-16 prob.tex
prob.tex \section{Proofs} Typing random conjecture, and think how to glue them together...

\begin{thm}\label{thm:analogTheorem23RichmanBridges1999}~
\begin{itemize}
\item Let $f:S^{2}\rightarrow\mathbb{R}$ be a bounded continuous approximation
frame function of weight~$\left(W_{l},W_{r}\right)$, $W=\frac{W_{l}+W_{r}}{2}$, 
\item $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{0}$,
$\ket{1}=\ket{2}\times\ket{0}$, 
\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
and 
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in S^{2}$..\qed\end{thm}
\begin{proof}
Let $\ket{\bar{2}}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{\bar{0}}$.
Then 
\[
\left|\left(f\left(\ket{0}\right)+f\left(\ket{2}\right)\right)-\left(f\left(\ket{\bar{0}}\right)+f\left(\ket{\bar{2}}\right)\right)\right|\le W_{r}-W_{l}
\]
so
\[
f\left(\ket{\bar{2}}\right)-f\left(\ket{2}\right)\ge f\left(\ket{0}\right)-f\left(\ket{\bar{0}}\right)-\left(W_{r}-W_{l}\right)=M-m-\left(W_{r}-W_{l}\right)
\]
whence $f\left(\ket{2}\right)\le m+W_{r}-W_{l}$. Let $\left(x,y,z\right)=\left(\ip{\psi}{0},\ip{\psi}{1},\ip{\psi}{2}\right)$
denote the coordinates of a point~$\ket{\psi}$ with respect to the
frame~$\left\{ \ket{i}\right\} _{i=0}^{2}$, then $Q\left(\ket{\psi}\right)=Mx^{2}+\left(W-M-m\right)y^{2}+mz^{2}$.

@@

\begin{thm}\label{thm:analogTheorem3.5Gleason1957}~
\begin{itemize}
\item Let $f:\mathbb{C}S^{2}\rightarrow\mathbb{R}$ be a bounded continuous
approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$. Recall $f$ could be uniquely extended
to the whole space~$\mathbb{C}^{3}$ by $f\left(0\right)=0$ and
$f\left(\ket{\psi}\right)=\left\Vert \ket{\psi}\right\Vert ^{2}f\left(\left\Vert \ket{\psi}\right\Vert ^{-1}\ket{\psi}\right)$
for nonzero vector~$\ket{\psi}$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in\mathbb{C}S^{2}$.\qed\end{thm}
\begin{proof}
This proof will be separated into two parts. The first part will estimate
the error between the approximation frame function and the quadratic
form on every complex two-space. The second part will then verify
the quadratic forms in the first part could be connected and get a
quadratic form on the whole space.

\begin{claim}For any pair of vectors~$\ket{\psi_{0}},\ket{\psi_{1}}\in\mathbb{C}S^{2}$. 
\begin{itemize}
\item Consider the complex vector space spanned by $\ket{\psi_{0}}$ and
$\ket{\psi_{1}}$, and $\mathbb{C}S^{1}$ be its unit sphere, i.e.,
\[
\left\{ \alpha_{0}\ket{\psi_{0}}+\alpha_{1}\ket{\psi_{1}}\middle|\alpha_{0},\alpha_{1}\in\mathbb{C}\textrm{ and }\left|\alpha_{0}\right|^{2}+\left|\alpha_{1}\right|^{2}=1\right\} \textrm{ .}
\]
\item $M=\max_{\ket{\psi}\in\mathbb{C}S^{1}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$.
\item $\ket{1}\in\mathbb{C}S^{1}$ is orthogonal to $\ket{0}$.
\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M\right)\ip{1}{\psi}^{2}$.
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in\mathbb{C}S^{1}$.\qed\end{claim}
\begin{proof}
For all $\ket{\psi}\in\mathbb{C}S^{1}$, 
\begin{eqnarray*}
 &  & \left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\\
 & = & \left|Q\left(\ket{\psi}\right)-f\left(\ket{0}\ip{0}{\psi}+\ket{1}\ip{1}{\psi}\right)\right|\\
 & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\left(\ket{0}\ip{0}{\psi}+\ket{1}\ip{1}{\psi}\right)\right)\right|\\
 & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\ket{0}\left|\ip{0}{\psi}\right|+\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\left|\ip{1}{\psi}\right|\right)\right|\\
 & \le & 27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)
\end{eqnarray*}
where the last inequality holds because $\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\in\mathbb{C}S^{1}$
is orthogonal to $\ket{0}$, $\bra{0}\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)=1\in\mathbb{R}$,
and 
\[
\left(\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\right)^{\dagger}\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)=\frac{\ip{\psi}{1}}{\left|\ip{\psi}{1}\right|}\frac{\left|\ip{\psi}{0}\right|}{\ip{\psi}{0}}\bra{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\in\mathbb{R}\textrm{ .}
\]
\end{proof}
\end{proof}

>>>>

\begin{thm}\label{thm:analogTheorem23RichmanBridges1999}~
\begin{itemize}
\item Let $f:S^{2}\rightarrow\mathbb{R}$ be a bounded continuous approximation
frame function of weight~$\left(W_{l},W_{r}\right)$, $W=\frac{W_{l}+W_{r}}{2}$, 
\item $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{0}$,
$\ket{1}=\ket{2}\times\ket{0}$, 
\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
and 
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in S^{2}$.\qed\end{thm}
\begin{proof}
Let $\ket{\bar{2}}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{\bar{0}}$.
Then 
\[
\left|\left(f\left(\ket{0}\right)+f\left(\ket{2}\right)\right)-\left(f\left(\ket{\bar{0}}\right)+f\left(\ket{\bar{2}}\right)\right)\right|\le W_{r}-W_{l}
\]
so
\[
f\left(\ket{\bar{2}}\right)-f\left(\ket{2}\right)\ge f\left(\ket{0}\right)-f\left(\ket{\bar{0}}\right)-\left(W_{r}-W_{l}\right)=M-m-\left(W_{r}-W_{l}\right)
\]
whence $f\left(\ket{2}\right)\le m+W_{r}-W_{l}$. Let $\left(x,y,z\right)=\left(\ip{\psi}{0},\ip{\psi}{1},\ip{\psi}{2}\right)$
denote the coordinates of a point~$\ket{\psi}$ with respect to the
frame~$\left\{ \ket{i}\right\} _{i=0}^{2}$, then $Q\left(\ket{\psi}\right)=Mx^{2}+\left(W-M-m\right)y^{2}+mz^{2}$.

@@

\yutsung{

\begin{thm}\label{thm:analogTheorem3.5Gleason1957}~
\begin{itemize}
\item Let $f:\mathbb{C}S^{2}\rightarrow\mathbb{R}$ be a bounded continuous
approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$. Recall $f$ could be uniquely extended
to the whole space~$\mathbb{C}^{3}$ by $f\left(0\right)=0$ and
$f\left(\ket{\psi}\right)=\left\Vert \ket{\psi}\right\Vert ^{2}f\left(\left\Vert \ket{\psi}\right\Vert ^{-1}\ket{\psi}\right)$
for nonzero vector~$\ket{\psi}$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in\mathbb{C}S^{2}$.\qed\end{thm}
\begin{proof}
~

\begin{claim}For any pair of orthogonal vectors~$\ket{\psi_{0}}$,
$\ket{\psi_{1}}$, and $\ket{\psi_{2}}\in\mathbb{C}S^{2}$. Consider
the real vector space spanned by them, and $S^{1}$ be its unit sphere,
i.e., 
\[
\left\{ \sum_{i=0}^{2}a_{i}\ket{\psi_{i}}\middle|a_{i}\in\mathbb{R}\textrm{ and }\sideset{_{\mathbb{R}}}{_{i=0}^{2}}\sum\left|\alpha_{i}\right|^{2}=1\right\} \textrm{ .}
\]

\begin{itemize}
\item $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{0}$,
$\ket{1}=\ket{2}\times\ket{0}$, 
\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
and 
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in S^{2}$. \qed\end{claim}
\begin{proof}
Direct from theorem~\ref{thm:analogTheorem23RichmanBridges1999}.
\end{proof}
\begin{claim}~
\begin{itemize}
\item $M=\max_{\ket{\psi}\in\mathbb{C}S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
$m=\min_{\ket{\psi}\in\mathbb{C}S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{0}$,
$\ket{1}=\ket{2}\times\ket{0}$, 
\item $Q\left(\ket{\psi}\right)=\bra{\psi}\left[M\proj{0}+\left(W-M-m\right)\proj{1}+m\proj{2}\right]\ket{\psi}$,
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
and 
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in S^{2}$. \qed\end{claim}
\begin{proof}
...................?

This proof will be separated into two parts. The first part will estimate
the error between the approximation frame function and the quadratic
form on every complex two-space. The second part will then verify
the quadratic forms in the first part could be connected and get a
quadratic form on the whole space.
\end{proof}
\begin{claim}For any pair of orthogonal vectors~$\ket{\psi_{0}},\ket{\psi_{1}}\in\mathbb{C}S^{2}$. 
\begin{itemize}
\item Consider the complex vector space spanned by $\ket{\psi_{0}}$ and
$\ket{\psi_{1}}$, and $\mathbb{C}S^{1}$ be its unit sphere, i.e.,
\[
\left\{ \alpha_{0}\ket{\psi_{0}}+\alpha_{1}\ket{\psi_{1}}\middle|\alpha_{0},\alpha_{1}\in\mathbb{C}\textrm{ and }\left|\alpha_{0}\right|^{2}+\left|\alpha_{1}\right|^{2}=1\right\} \textrm{ .}
\]
\item $\ket{\psi_{2}}=\ket{\psi_{0}}\times\ket{\psi_{1}}\in\mathbb{C}S^{2}$.
\item $M=\max_{\ket{\psi}\in\mathbb{C}S^{1}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$.
\item $\ket{1}\in\mathbb{C}S^{1}$ is orthogonal to $\ket{0}$.
\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M\right)\ip{1}{\psi}^{2}$.
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in\mathbb{C}S^{1}$.\qed\end{claim}
\begin{proof}
For all vector~$\ket{\psi}\in\mathbb{C}S^{1}$, 
\begin{eqnarray*}
 &  & \left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\\
 & = & \left|Q\left(\ket{\psi}\right)-f\left(\ket{0}\ip{0}{\psi}+\ket{1}\ip{1}{\psi}\right)\right|\\
 & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\left(\ket{0}\ip{0}{\psi}+\ket{1}\ip{1}{\psi}\right)\right)\right|\\
 & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\ket{0}\left|\ip{0}{\psi}\right|+\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\left|\ip{1}{\psi}\right|\right)\right|\\
 & \le & 27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)
\end{eqnarray*}
where the last inequality holds because $\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\in\mathbb{C}S^{1}$
is orthogonal to $\ket{0}$, $\bra{0}\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)=1\in\mathbb{R}$,
and 
\[
\left(\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\right)^{\dagger}\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)=\frac{\ip{\psi}{1}}{\left|\ip{\psi}{1}\right|}\frac{\left|\ip{\psi}{0}\right|}{\ip{\psi}{0}}\bra{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\in\mathbb{R}\textrm{ .}
\]
\end{proof}
\end{proof}
}
